---
title: "HW4"
author: "Zachary Weitzman"
date: "2023-02-08"
output: html_document
---
# <span style="color:blue">HW4</span>
## <span style="color:red">Number 1</span>
```{r}
x<-1.1
a<-2.2
b<-3.3
z<-x^a^b
print(z)
z<-(x^a)^b
print(z)
z<-3*x^3 + 2*x^2 +1
print(z)
```
Using a carrot makes exponents, the asterisks is for multiplying a digit and a saved value.

## <span style="color:red">Number 2</span>
```{r}
s1<-seq(1,8)
s2<-seq(7,1)
s3<-c(s1,s2)
print(s3)
g<-c(1:5)
rep(g, times=g)
f<-c(5:1)
rep(f, times=g)
```
For the first, by creating a forward sequence and a backward sequence and combining I could create the desired sequence. The second I needed to 'times' each by the corresponding number in the vector. The same happened for the last except I used a new sequence from 5 to 1.

## <span style="color:red">Number 3</span>
```{r}
xcoord<-runif(1,1,10)
ycoord<-runif(1,1,10)
theta<-atan(ycoord/xcoord)
r<-ycoord/sin(theta)
print(r)
print(theta)
```
Taking the x and y-coords I solved for sin and cos of theta which equals y/r and x/r repectivly. Knowing that tan(theta) equals sin(theta)/cos(theta), than yr/xr=tan(theta). the r's cancel and y/x=tan(theta) using inverse tangent I found theta and used it to find r.

## <span style="color:red">Number 4</span>
```{r}
queue<-c("sheep","fox", "owl", "ant")
queue1<-c(queue,"serpent")
queue2<-queue1[!queue1=="sheep"]
queue3<-c("donkey",queue2)
queue4<-queue3[!queue3=="serpent"]
queue5<-queue4[!queue4=="owl"]
queue6<-c(queue5[!queue5=="ant"],"aphid","ant")
which(queue6=="aphid")
```
By creating a new queue vector which the changes are concatenated in or removed by recalling everything from the last queue vector except for the unwanted animal. Then using the which() function I can determine aphids position in the vector.

## <span style="color:red">Number 5</span>
```{r}
nums<-1:100
nums2<-nums[nums%%2 & nums%%3 & nums%%7 !=0]
print(nums2)
```
First I created a vector with numbers 1 to 100. I then created a new vector same as the old except every number was divided by 2, 3 and 7 and only those numbers whose remainder was not equal to zero were kept.
