---
title: "HW7"
author: "Zachary Weitzman"
date: "2023-03-08"
output: html_document
---
```{r}
#library(ggplot2)
#library(MASS)
#library(tidyverse)
z <- rnorm(n=3000,mean=0.2)
z <- data.frame(1:3000,z)
names(z) <- list("ID","myVar")
z <- z[z$myVar>0,]
str(z)
summary(z$myVar)
p1 <- ggplot(data=z, aes(x=myVar, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",linewidth=0.2)
print(p1)
```
```{r}
p1 <-  p1 +  geom_density(linetype="dotted",size=0.75)
print(p1)
```
```{r}
normPars <- fitdistr(z$myVar,"normal")
print(normPars)
str(normPars)
normPars$estimate["mean"]# note structure of getting a named attribute

meanML <- normPars$estimate["mean"]
sdML <- normPars$estimate["sd"]

xval <- seq(0,max(z$myVar),len=length(z$myVar))

stat <- stat_function(aes(x = xval, y = ..y..), fun = dnorm, colour="red", n=length(z$myVar), args = list(mean = meanML, sd = sdML))
p1 + stat

expoPars <- fitdistr(z$myVar,"exponential")
rateML <- expoPars$estimate["rate"]

stat2 <- stat_function(aes(x = xval, y = ..y..), fun = dexp, colour="blue", n = length(z$myVar), args = list(rate=rateML))
p1 + stat + stat2

stat3 <- stat_function(aes(x = xval, y = ..y..), fun = dunif, colour="darkgreen", n = length(z$myVar), args = list(min=min(z$myVar), max=max(z$myVar)))
p1 + stat + stat2 + stat3

gammaPars <- fitdistr(z$myVar,"gamma")
shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]

stat4 <- stat_function(aes(x = xval, y = ..y..), fun = dgamma, colour="brown", n = length(z$myVar), args = list(shape=shapeML, rate=rateML))
p1 + stat + stat2 + stat3 + stat4

pSpecial <- ggplot(data=z, aes(x=myVar/(max(myVar + 0.1)), y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) + 
  xlim(c(0,1)) +
  geom_density(size=0.75,linetype="dotted")

betaPars <- fitdistr(x=z$myVar/max(z$myVar + 0.1),start=list(shape1=1,shape2=2),"beta")
shape1ML <- betaPars$estimate["shape1"]
shape2ML <- betaPars$estimate["shape2"]
statSpecial <- stat_function(aes(x = xval, y = ..y..), fun = dbeta, colour="orchid", n = length(z$myVar), args = list(shape1=shape1ML,shape2=shape2ML))

pSpecial + statSpecial



colony <- read.table("Colony.csv",header=TRUE,sep=",")
colony$TotalL<-as.numeric(colony$TotalL)
colony<-colony[1:150,]
ot<-ggplot(data=colony, aes(x=TotalL, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",linewidth=0.2,binwidth=5)
print(ot)
ot <-  ot +  geom_density(linetype="dotted",size=0.75)
print(ot)
normParz <- fitdistr(colony$TotalL,"normal")
print(normParz)
str(normParz)
normParz$estimate["mean"]# note structure of getting a named attribute
meancolony<- normParz$estimate["mean"]
sdcolony<- normParz$estimate["sd"]
colval <- seq(0,max(colony$TotalL),len=length(colony$TotalL))
statc<- stat_function(aes(x = colval, y = ..y..), fun = dnorm, colour="red", n=length(colony$TotalL), args = list(mean = meancolony, sd = sdcolony))
ot + statc
expoParz<-fitdistr(colony$TotalL,"exponential")
ratecolony <- expoParz$estimate["rate"]
statc2 <- stat_function(aes(x = colval, y = ..y..), fun = dexp, colour="blue", n = length(colony$TotalL), args = list(rate=ratecolony))
ot + statc + statc2

statc3 <- stat_function(aes(x = colval, y = ..y..), fun = dunif, colour="darkgreen", n = length(colony$TotalL), args = list(min=min(colony$TotalL), max=max(colony$TotalL)))
ot + statc + statc2 + statc3

gammaParz <- fitdistr(colony$TotalL,"gamma")
shapecolony <- gammaParz$estimate["shape"]
ratecolony <- gammaParz$estimate["rate"]

statc4 <- stat_function(aes(x = colval, y = ..y..), fun = dgamma, colour="brown", n = length(colony$TotalL), args = list(shape=shapecolony, rate=ratecolony))
ot + statc + statc2 + statc3 + statc4
colSpecial <- ggplot(data=colony, aes(x=TotalL/(max(TotalL + 0.1)), y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) + 
  xlim(c(0,1)) +
  geom_density(size=0.75,linetype="dotted")
betaParz <- fitdistr(x=colony$TotalL/max(colony$TotalL + 0.1),start=list(shape1=1,shape2=2),"beta")
shape1col <- betaParz$estimate["shape1"]
shape2col <- betaParz$estimate["shape2"]
statcolSpecial <- stat_function(aes(x = colval, y = ..y..), fun = dbeta, colour="orchid", n = length(colony$TotalL), args = list(shape1=shape1col,shape2=shape2col))

colSpecial + statcolSpecial
```
A normal distribution fits best on my Data
```{r}
simcol<-data.frame(1:150,rnorm(n=150,mean=meancolony,sd=sdcolony))
simcol$valz<-simcol$rnorm.n...150..mean...meancolony..sd...sdcolony.
simplot<-ggplot(data=simcol,aes(x=valz,y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",linewidth=0.2,binwidth=5)
simden<-simplot +geom_density(linetype="dotted",size=0.75)
simden
ot
```
The two histogram profiles look very similar, but the simulated data is much broader than the real data. This is because the real data was more of a t-distribution than a normal distribution which meant that it had a sharper peak than the simulation. Even so, I think that the simulation does a pretty good job simulating realistic data, because the two did not differ enough to skew the data too much.